Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-01-16 4.exact_support_recovery/4.phase_transition_results.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > g(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}

\begin{corollary}[Classes of procedures attaining the boundary]
\label{cor:FWER-controlling_procedures}  
Relation \eqref{eq:exact-supporot-recovery} holds for any FWER-controlling procedure that is strictly more powerful than Bonferroni's procedure. 
This includes Holm's procedure \citep*{holm1979simple}, and in the case of independent errors, Hochberg's procedure \citep*{hochberg1988sharper}, and the {\v{S}}id{\'a}k procedure \citep*{vsidak1967rectangular}.
\end{corollary}

\begin{example} \label{exmp:FWER-controlling_procedures}
Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of $(\log{p})^{-1/2}$, and hence Theorem \ref{thm:sufficient} applies. 
By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.
\end{example}

%Proof of Theorem \ref{thm:sufficient} is found in Section \ref{sec:proofs}, 
The claims in Example \ref{exmp:FWER-controlling_procedures} are verified in Section \ref{suppsec:proofs}.

We now turn to the proof of Theorem \ref{thm:sufficient}.

\begin{proof}[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:optimality} below.

@@

\begin{theorem} \label{thm:necessary}
    Let ${\cal E}$ be a triangular array with common $\text{AGG}(\nu)$ marginal $F$, $\nu > 0$.
    % Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries where $\beta\in(0,1]$, where the signal sizes $\mu(i)$, $i\in S_p$ are at most $\overline{\Delta} = \left(\nu\overline{r}\log p\right)^{1/\nu}$.
    % and the signals $\mu$ have $s=|S|=\lfloor p^{1-\beta}\rfloor$ be as described in Theorem \ref{thm:sufficient}. 
    Assume further that the errors ${\cal E}$ have uniform relatively stable maxima and minima, i.e., ${\cal E}\in U(F)$, and $(-{\cal E}) = \{-\epsilon_{p}(i)\} \in U(F)$.
    If 
    \begin{equation} \label{eq:signal-below-boundary}
        \overline{r} < g(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
    \end{equation}
    then
    \begin{equation} \label{eq:classification-impossible-dependent}
        \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^-(\beta, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
    \end{equation}
    where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}

% We comment on some consequences of the theorem, before presenting its proof.
Our first comment is on the signal sizes, and in particular, the gap between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary conditions (Theorem \ref{thm:necessary}).

\begin{remark} \label{rmk:gap-between-sufficient-necessary}
The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in Example \ref{exmp:signals-straddling-the-boundary} below.
\end{remark}

@@

Consider two scenarios
\begin{enumerate}
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
\end{enumerate}
for some constants $0<\delta<1-\beta<1$. 
In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.
\end{example}
The claims in Example \ref{exmp:signals-straddling-the-boundary} are verified in Section \ref{suppsec:proofs}.

@@

Theorem \ref{thm:necessary} also yields an answer the question raised in \citet{butucea2018variable}.
In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
errors (see \cite{hall2010innovated}). 
Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}. Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.

To facilitate comparison with results in existing literature, we will formulate explicit minimax statements in Section \ref{sec:optimality}.
\end{remark}

We must emphasize that the restriction to the URS dependence class is \emph{not} an assumption of convenience. 
The condition on dependence characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.

@@

We conclude with the proof of Theorem \ref{thm:necessary}.

\begin{proof} [Proof of Theorem \ref{thm:necessary}]
To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.

>>>>

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > g(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

\medskip
We end this section with several comments and applications of Theorem \ref{thm:sufficient}.
\begin{corollary}[Classes of procedures attaining the boundary]
\label{cor:FWER-controlling_procedures}  
Relation \eqref{eq:exact-supporot-recovery} holds for any FWER-controlling procedure that is strictly more powerful than Bonferroni's procedure. 
This includes Holm's procedure \citep*{holm1979simple}, and in the case of independent errors, Hochberg's procedure \citep*{hochberg1988sharper}, and the {\v{S}}id{\'a}k procedure \citep*{vsidak1967rectangular}.
\end{corollary}

\begin{example} \label{exmp:FWER-controlling_procedures}
Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of ${\cal O}((\log{p})^{-1/2})$, and hence Theorem \ref{thm:sufficient} applies. 
By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.

\begin{proof}[Example \ref{exmp:FWER-controlling_procedures}]
By the Mill's ratio for the standard Gaussian distribution,
$$
\frac{t_p \P\left[Z>t_p\right]}{\phi(t_p)} \to 1,\quad \text{as}\quad t_p\to\infty,
$$
where $Z\sim \text{N}(0,1)$. 
Using the expression for $t_p = \sqrt{2\log{p}}$, we have
$$
p \;\P\left[Z>t_p\right] \sim \sqrt{2\pi}^{-1}\left(2\log{p}\right)^{-1/2} \to 0,
$$
as desired. The rest of the claims follow from Corollary \ref{cor:FWER-controlling_procedures}.
\end{proof}
\end{example}

The statements in Theorem \ref{thm:sufficient} can be strengthened, to prepare us for a minimax result given in Section \ref{sec:minimax} below.

@@

\begin{theorem} \label{thm:necessary}
    Let ${\cal E}$ be a triangular array with common $\text{AGG}(\nu)$ marginal $F$, $\nu > 0$.
    % Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries where $\beta\in(0,1]$, where the signal sizes $\mu(i)$, $i\in S_p$ are at most $\overline{\Delta} = \left(\nu\overline{r}\log p\right)^{1/\nu}$.
    % and the signals $\mu$ have $s=|S|=\lfloor p^{1-\beta}\rfloor$ be as described in Theorem \ref{thm:sufficient}. 
    Assume further that the errors ${\cal E}$ have uniform relatively stable maxima and minima, i.e., ${\cal E}\in U(F)$, and $(-{\cal E}) = \{-\epsilon_{p}(i)\} \in U(F)$.
    If 
    \begin{equation} \label{eq:signal-below-boundary}
        \overline{r} < g(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
    \end{equation}
    then
    \begin{equation} \label{eq:classification-impossible-dependent}
        \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^-(\beta, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
    \end{equation}
    where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}
\begin{proof} %[Proof of Theorem \ref{thm:necessary}]
To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.

% We comment on some consequences of the theorem, before presenting its proof.
We end this section with several remarks on the scope and consequences
of our results. Our first comment is on the signal sizes, and in particular, the gap 
between the sufficient conditions (Theorem \ref{thm:sufficient}) and the necessary 
conditions (Theorem \ref{thm:necessary}).

\begin{remark}[Minding the gap] \label{rmk:gap-between-sufficient-necessary}
The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in 
Example \ref{exmp:signals-straddling-the-boundary} below.
\end{remark}

@@

Consider two scenarios
\begin{enumerate}
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
\end{enumerate}
for some constants $0<\delta<1-\beta<1$. 
In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.

\begin{proof}[Example \ref{exmp:signals-straddling-the-boundary}]
In the first scenario, signal sizes in $S^{(1)}_p$ are by definition above the strong classification boundary \eqref{eq:strong-classification-boundary}.
The signal in $S^{(2)}_p$ has size parameter $1+\delta<2-\beta<(1+\sqrt{1-\beta})^2$, and therefore falls below the boundary.

It remains to show that $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$.
To do so, we define two new arrays 
$$
{\cal Y}^{(k)} = \{y^{(k)}_p(j),\;j=1,2,\ldots,p\},\quad k\in\{1,2\}_p,
$$
where $y^{(k)}_p(j)=x_p(j)$ if $j\not\in S^{(k)}_p$, and $y^{(k)}_p(j)=\widetilde{\epsilon}_p(j)$ if $j\in S^{(k)}_p$, using an independent error array $\{\widetilde{\epsilon}_p(j),\;j=1,\ldots,p\}$ with iid standard Gaussian elements.
That is, we replace the elements in $S^{(1)}_p$ and $S^{(2)}_p$ with iid standard Gaussian noise.
Notice both arrays ${\cal Y}^{(1)}$ and ${\cal Y}^{(2)}$ satisfy the conditions in Theorem \ref{thm:sufficient} (with sparsity parameter equal to $\beta$ and $1$, respectively). 
Hence, we have
$$
\P[\widehat{S}^{\text{Bonf}}_p\subseteq S_p] 
= \P\left[\max_{j\in S^c}x(j) \le t_p\right]
\le \P\left[\max_{j\in S^c}y^{(1)}(j) \le t_p\right] \to 0,
$$
and 
\begin{align*}
    \P[\widehat{S}^{\text{Bonf}}_p\supseteq S_p]
    &= \P\left[\min_{j\in S}x(j) > t_p\right] 
    \ge 1 - \P\left[\min_{j\in S^{(1)}}x(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}x(j) \le t_p\right] \\
    &\ge 1 - \P\left[\min_{j\in S^{(1)}}y^{(2)}_p(j) \le t_p\right] - \P\left[\min_{j\in S^{(2)}}y^{(1)}_p(j) \le t_p\right] 
    \to 1,
\end{align*}
where $t_p$ is the threshold in Bonferroni's procedure. The conclusion follows.
% only need to show $\mathbb{P}[S^{(2)}_p\subseteq\widehat{S}^{\text{Bonf}}_p]\to 1$.

In the second scenario, the signal sizes in $S^{(2)}$ by definition fall below the strong classification boundary \eqref{eq:strong-classification-boundary}.
To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
In particular, we obtain
$$
    \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
$$
By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
\begin{equation}
\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
\end{equation}
where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
\begin{align*}
    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
\end{align*}
where we used the URS of the error arrays, and that 
$$
u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
$$
to conclude the convergence in probability.
\end{proof}
\end{example}

@@

Theorem \ref{thm:necessary} answers a question raised in \citet{butucea2018variable}.
In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
errors \citep{hall2010innovated}. 
Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}. Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
For more details, see also Section \ref{sec:minimax}.
\end{remark}

\begin{remark} We emphasize that the restriction to the URS dependence class in Theorem \ref{thm:necessary} is 
\emph{not} an assumption of convenience. 
The dependence condition characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
\end{remark}

@@

### 2021-01-16 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
update
cleaned up Ch 4.

Both (new) Ch 4 and 5 are ready to re-read.

Finally, we offer some insights into the support recovery problem in the case when errors have heavier-than-exponential tails in Section \ref{subsec:optimal-procedure-super-exponential}.

@@

In studying support recovery problems (e.g., \citet{arias2017distribution}), restrictions to the thresholding procedures are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
%  In Theorem \ref{thm:sufficient} we saw that a (FWER-controlling) thresholding procedure is indeed consistent for support recovery. 
% It is natural to ask if it will be sufficient to restrict our attention to only such procedures.
We show in this section that, perhaps surprisingly, for general error models, thresholding procedures are not always optimal, even when the observations are independent.

@@

If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics.

\stilian{\fbox{COMMENT} Just like for the likelihood thresholding procedure, we should be more careful about the ties and how to define
the oracle thresholding procedure so that $\widehat{S}^*$ has exactly $s$ elements.  I propose the following change}{\, }

\stilian{

For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
$$
\langle a_1,\cdots,a_s\rangle := (a_{[1]},\cdots,a_{[s]})
$$
denote the vector of $a_i$'s arranged in a non-increasing order.

@@

\subsection{When is oracle thresholding Bayes optimal?} % under sub-exponential errors}
\label{subsec:optimal-procedure-sub-exponential}

An elegant answer of this question can be given in terms of the \emph{monotone likelihood ratio} (MLR) property.

@@

The following result provides a general criterion for the finite-sample optimality of the oracle thresholding 
procedure $\widehat{S}^*$.

@@

\stilian{COMMENT}{Consider moving the following discussion \& theorem to the section on Minimax below...}

Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
necessary condition of support recovery, with the help of Proposition \ref{prop:log-concave}, can be 
strengthened to include all procedures (in the Bayesian context), regardless of whether they are thresholding.

\subsection{Bayes optimality of likelihood ratio thresholding}
\label{subsec:optimal-procedure-super-exponential}

@@

\subsection{Sub-optimality of data thresholding procedures}\label{sec:sup-optimality-of-thresholding}

@@

\section{Minimax optimality in exact support recovery}

We establish in this section minimax versions of our results from Chapter \ref{chap:exact-support-recovery}.
Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structures in the URS class.
This is formalized in Corollary \ref{cor:point-wise-minimax} below.% in Section \ref{subsec:point-wise-minimax}.
We refer to this result as \emph{point-wise} minimax, to emphasize the fact that this optimality holds for every \emph{fixed} URS array.

@@

@@

  \stilian{Here we briefly discuss the optimality and sub-optimality of the 
 thresholding procedures.}{Needs work}

%\begin{remark} \label{rmk:tail-assumptions}

Consider the model \eqref{eq:model-additive} with independent errors, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.

@@

\begin{table}[ht]
    \centering
    \caption{Properties of thresholding procedures under different error distributions when errors are independent. Properties of the error distributions are listed in brackets.}
    \medskip
    \begin{tabular}{p{45mm}p{40mm}p{40mm}} \toprule
        Thresholding procedure & Bayes optimality &  Phase transition \\ 
        (Error distributions) &  (Log-concave density) & (Rapidly-varying tails) \\ \midrule
        AGG($\nu$), $\nu\ge1$ & Yes (Yes) & Yes (Yes) \\ \cmidrule{1-3}
        AGG($\nu$), $0<\nu<1$ & No (No) & Yes (Yes) \\ \cmidrule{1-3}
        Power laws & No (No) & No (No) \\ \bottomrule
    \end{tabular}
    \label{table:role-of-thresholding}
\end{table}

>>>>

In this chapter, we investigate the universality of the phase-transition results on exact support recovery established in
Chapter \ref{chap:exact-support-recovery}.  Specifically, we would like to know to what extent the signal classification 
boundary valid for thresholding estimators applies to the best possible support estimators.  The answer to this question 
will complete the characterization of the fundamental limits in exact support recovery.

To this end, we begin by characterizing the finite-sample Bayes optimality of the thresholding procedures (Section
\ref{subsec:optimal-procedure-sub-exponential}). As we will see, the so-called oracle thresholding estimators are in 
fact finite-sample optimal for certain classes of models.  These optimality results allow us to establish 
powerful minimax formulations of the exact support recovery phase-transition phenomenon showing its universality for all estimators (Theorem \ref{thm:necessary-strengthened}).

Perhaps surprisingly, however, thresholding estimators can be sub-optimal.  This is so for example 
in the additive noise model with heavier than exponential error densities (Example 
\ref{exmp:suboptimal-data-thresholding}).   In this case, the likelihood ratio
thresholding rather than data thresholding can lead to optimal support estimators
(Section \ref{subsec:optimal-procedure-super-exponential}).  In such cases, the universality 
of the exact support recovery boundary remains an open question.

@@

In studying support recovery problems \citep[e.g.,][]{arias2017distribution}, restrictions to the thresholding procedures 
are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set.
We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
optimal, even when the observations are independent.

@@

If, however, the sparsity $s = |S|$ of the problem is known, then a natural estimator for $S$ would be based on the set of top $s$ order statistics. Such estimators will be referred to as oracle thresholding estimators and formally defined next.

\stilian{ 
For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
$$
\langle a_1,\cdots,a_s\rangle := (a_{[1]},\cdots,a_{[s]})
$$
denote the vector of $a_i$'s arranged in a non-increasing order.

@@

\section{Bayes optimality of oracle thresholding} % under sub-exponential errors}
\label{subsec:optimal-procedure-sub-exponential}

In this section, we study the Bayes optimality of the oracle thresholding procedures.  
The following \emph{monotone likelihood ratio} (MLR) property will play a key role.

@@

The next result provides a general criterion for the finite-sample Bayes optimality of the oracle thresholding 
procedure $\widehat{S}^*$.

@@

\section{Bayes optimality of likelihood ratio thresholding}
\label{subsec:optimal-procedure-super-exponential}

@@

\section{Sub-optimality of data thresholding procedures}\label{sec:sup-optimality-of-thresholding}

@@

\section{Minimax optimality in exact support recovery} \label{sec:minimax}

We establish in this section minimax versions of our results from Chapter \ref{chap:exact-support-recovery}.
Specifically, if we restrict ourselves to \emph{the class of thresholding procedures} $\cal T$ (defined in \eqref{eq:thresholding-procedure}), then Bonferroni's procedure is minimax optimal, for \emph{any} fixed dependence structure in the URS class.
This is formalized in Corollary \ref{cor:point-wise-minimax} below.% in Section \ref{subsec:point-wise-minimax}.
We refer to this result as \emph{point-wise} minimax, to emphasize the fact that this optimality holds for every \emph{fixed} URS array.

@@

Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Proposition 
\ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
of whether they are thresholding or not.

@@

\stilian{NEEDS}{WORK}

Consider the model \eqref{eq:model-additive} with independent errors. Theorem \ref{thm:necessary-strengthened} 
and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty in the exact support 
recovery problem, in the regime when the thresholding estimators are optimal. Specifically, in such cases the signal classification boundary is universal.

 Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are in fact \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$.
Therefore, the optimality of thresholding procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.

@@

\begin{table}[ht]
    \centering
    \caption{Properties of thresholding procedures under different error distributions when errors are independent. Properties of the error distributions are listed in brackets.}
    \medskip
    \begin{tabular}{p{40mm}p{37mm}p{37mm}} \toprule
        Thresholding procedure & Bayes optimality &  Phase transition \\ 
        (Error distributions) &  (Log-concave density) & (Rapidly-varying tails) \\ \midrule
        AGG($\nu$), $\nu\ge1$ & Yes (Yes) & Yes (Yes) \\ \cmidrule{1-3}
        AGG($\nu$), $0<\nu<1$ & No (No) & Yes (Yes) \\ \cmidrule{1-3}
        Power laws & No (No) & No (No) \\ \bottomrule
    \end{tabular}
    \label{table:role-of-thresholding}
\end{table}
